Chemical tagging: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-13 papers/clusters.tex
outline, text

\section{Data and method}

@@

DWH: Clustering methodology.

\section{Results and discussion}

>>>>

DWH: Think of this as a hypothesis test.

\section{Sample and abundances}

@@

\section{Method and results}

Although only hints of small-scale clustering in the abundance space
are visible in \figurename~DWH, exploration of the data indicates that
known clusters do appear in the abundance space as over-densities.
This encourages us to look for over-densities automatically in the
abundance space and see if anything found that way would be over-dense
in phase space.
The simplest method for clustering points in $D$-dimensional space is
the \emph{k-means} algorithm (DWH CITE).
This algorithm is fast and performs well in practice in problems of
this nature.

DWH: Scaling of the data
DWH: number of clusters
DWH: restarts for local minima

DWH: Reminder that we don't need the absolute best clustering to
demonstrate the hypothesis.

\section{Discussion}
